### 2022-02-25 paper.tex
fixed FPTAS bound

\usepackage{hyperref}
\hyperbaseurl{}
\urlstyle{same}
\usepackage[ruled]{algorithm2e}
\newcommand{\lIfElse}[3]{\lIf{#1}{#2 \textbf{else}~#3}}

@@

An intuitive extension of the greedy algorithm for Alma's problem is to iteratively add to $\mathcal{X}$ the school $k$ for which $[ v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) ] / g_k$ is largest. However, this algorithm offers no guaranteed approximation ratio. 
% as the following example suggests ...The construction above shows that the objective function of Ellis's problem can approximate that of a knapsack problem with arbitrary precision, and this algorithm

\subsection{Pseudopolynomial-time dynamic program}
In this subsection, we provide an algorithmic solution to Ellis's problem that runs in $O(Hm + m\log m)$ time and $O(Hm)$ space. The algorithm resembles the dynamic programming algorithm for the binary knapsack problem. Because we cannot assume that $H \leq m$ (as was the case in Alma's problem), this represents a pseudopolynomial-time solution (Dantzig 1957; Garey and Johnson 1979; \emph{Wikipedia}, s.v. ``Knapsack problem'').

With minimal loss of generality, we assume that $g_j \in \mathbb{N}$ for $j = 1\dots m$ and $H \in\mathbb{N}$. For $j = 0 \dots m$ and $h = 0 \dots H$, let $\mathcal{X}[j, h]$ denote the optimal portfolio using only the schools $\{ 1, \dots, j\}$ and costing no more than $h$, and let $V[j,h] = v(\mathcal{X}[j, h])$.  It is clear that if $j=0$ or $h=0$, then $\mathcal{X}[j, h] = \O$ and $V[j, h] = 0$.  For convenience, we also define $V[j, h] = -\infty$ for all $h < 0$.

@@

\begin{proof}
Optimality follows from the foregoing discussion. Sorting by $t_j$ is $O(m \log m)$.  The number of indices at which $V(j, h)$ is nontrivially defined is $O(Hm)$. To prevent $V(j, h)$ from being evaluated more than once at a given index, its values can be stored in a dictionary as they are computed.
\end{proof}

@@

\subsection{Fully polynomial-time approximation scheme}
As with the knapsack problem, Ellis's problem admits a complementary dynamic program that iterates on the value of the cheapest portfolio instead of on the cost of the most valuable portfolio. We will use this algorithm as the basis for a fully polynomial-time approximation scheme for Ellis's problem.
%Now, we modify Algorithm \ref{ellisDP2} into a fully polynomial-time approximation scheme for Ellis's problem.
Here we assume only that is each $t_j$ is integral. We will represent the approximate value of each portfolio using a fixed-point decimal with a precision of $P$, where $P$ is the number of digits to retain after the decimal point. Since $t_m$ is a trivial upper bound on the value of any portfolio, the set of possible portfolio valuations is now finite: $\mathcal{V} = \{0, 1\times 10^{-P}, 2\times 10^{-P}, \dots, t_m - 1\times 10^{-P}, t_m\}$. Its cardinality is $|\mathcal{V} | = P t_m$. 
Let $r[x] = \lfloor 10^P x \rfloor 10^{-P}$ denote the value of $x$ rounded down to its nearest fixed-point representation.

For integers $0 \leq j \leq m$ and $v \leq t_m$, let $\mathcal{W}[j, v]$ denote the least expensive portfolio using only the schools $\{ 1, \dots, j\}$ and having value at least $v$, if such a portfolio exists. Let $G[j, v] = r\bigl[v(\mathcal{W}[j, v])\bigr]$ denote the fixed-point representation of the corresponding value, where $G[j, v] = \infty$ if $\mathcal{W}[j, v]$ does not exist. It is clear that if $v \leq 0$, then $\mathcal{W}[j, v] = \O$ and $G[j, h] = 0$. If $j = 0$ and $v > 0$, then $G[j, h] = \infty$.  For the remaining indices (where $j, v > 0$), we claim that
\begin{align} \label{recursionrelationforcostmindp}
G[j, v] &=
\begin{cases}
\infty, \quad & t_j < v \\
\min\bigl\{G[j-1, v], g_j + G[j-1, v - \Delta] \bigr\}, \quad & t_j \geq v 
%\begin{cases}
%\min\bigl\{G[j-1, v], g_j + G[j-1, v - \Delta] \bigr\}, \quad &f_j < 1 \\
%\min\bigl\{G[j-1, v], g_j \bigr\}, \quad &f_j = 1 \text{ and } f_j t_j \geq v\\
%G[j-1, v], \quad &f_j = 1 \text{ and } f_j t_j < v
\end{cases}\\
\text{where}\qquad
\Delta_j (v) &= 
\begin{cases}
r\left[\frac{f_j}{1 - f_j} (t_j - v)\right], \quad & f_j < 1\\
\infty, &f_j = 1
\end{cases} \label{deltajvdef}
\end{align}
In the $t_j < v$ case, any feasible portfolio must be composed of schools with utility less than $v$, and therefore its valuation can not equal $v$, meaning that $\mathcal{W}[j, v]$ is undefined. In the $t_j \geq v$ case, the first argument to $\min\{\}$ says simply that omitting $j$ and choosing $\mathcal{W}[j-1, v]$ is a feasible choice for $\mathcal{W}[j, v]$. If, on the other hand, $j \in \mathcal{W}[j, v]$, then
\begin{equation} \label{solvemeforvwjvminusj}
v(\mathcal{W}[j, v]) = (1 - f_j )v(\mathcal{W}[j, v]\setminus \{j\}) + f_j t_j\end{equation}
Therefore, the subportfolio $\mathcal{W}[j, v]\setminus \{j\}$ must have a value of at least $v - \Delta$, where $\Delta$ satisfies $v = (1 - f_j )(v - \Delta) + f_j t_j $. When $f_j < 1$, the solution to this equation is $ \Delta = \frac{f_j}{1 - f_j} (t_j - v)$. By rounding this value down, we ensure that the true valuation of $\mathcal{W}[j, v]$ is \emph{at least} $v - \Delta$.

@@

Once $G[j, v]$ has been calculated at each index, the corresponding portfolio can be found by applying the observation that $
\mathcal{W}[j, v]$ contains $j$ if and only if $G[j, v] < G[j-1, v]$. Then an approximate solution to Ellis's problem is obtained by applying this observation to the approximate optimal objective value $\max\{ w: G[m, w] \leq H\}$.

\begin{algorithm}[H] 
%\DontPrintSemicolon
\caption{Polynomial-time approximation scheme for Ellis's problem.} \label{ellisDP3}
\KwData{Utility values $t \in \mathbb{N}^m$, admissions probabilities $f \in (0, 1]^m$, application costs $g \in (0, \infty)^m$, budget $H \in (0, \infty)^m$, tolerance $\varepsilon \in (0, 1)$.}
Index schools in ascending order by $t$\;
$P \gets \bigl\lceil\log_{10}\left(m / \varepsilon f_m t_m\right)\bigr\rceil$\;
\SetKwProg{Fn}{function}{ do}{end}
\Fn{$G(j, v)$}{
	\lIf{$v \leq 0$}{\Return{$0$}}
	\lElseIf{$j=0$ or $t_j < v$}{\Return{$\infty$}}
	\Else {\Return{$\min\Bigl\{ G(j-1, v), g_j + G\bigl(j-1, v -  \Delta_j(v)\bigr) \Bigr\}$}}
}
%	\uIf{$f_j < 1$}{\Return{$\min\bigl\{ G(j-1, v), g_j + G(j-1, v -  \lfloor \frac{f_j}{1 - f_j} (t_j - v)\rfloor ) \bigr\}$}}
%	\uElseIf{$f_j = 1$ and $f_j t_j \geq v$}{\Return{$\min\bigl\{G[j-1, v], g_j \bigr\}$}}
%	\lElse{\Return{$G(j-1, v)$}}
%	}
%\lFor{$j=1\dots m$}
%{$\operatorname{push!}\bigl(\mathtt{H}, (j, f_j, t_j)\bigr)$}
%\For{$i=1\dots h$}
%{
%    $\mathtt{D} \gets \operatorname{pop!}(\mathtt{H})$\;
%    $\operatorname{append!}(\mathtt{X}, \mathtt{D.j})$\;
%     \lIfElse{$i=1$}{$\operatorname{append!}(\mathtt{V}, \mathtt{D.f}\cdot\mathtt{D.t})$}
%     {$\operatorname{append!}(\mathtt{V}, \mathtt{V[i-1]} + \mathtt{D.f}\cdot\mathtt{D.t})$}
%    \For{$\mathtt{E} \in \mathtt{H}$}
%	{
%	\lIfElse{$\mathtt{E.j} < \mathtt{D.j}$}{$\mathtt{E.t} \gets  \mathtt{E.t} \cdot(1 -  \mathtt{D.f})$}{$\mathtt{E.t} \gets  \mathtt{E.t} -  \mathtt{D.f}\cdot\mathtt{D.t}$}
%	}
%}
$v^* \gets  \max\{ w: G(m, w) \leq H\}$\;
$v \gets v^*$\;
$\mathcal{X} \gets \O$\;
\For{$j = m, m-1, \dots, 1$}{
	\If{$G(j, v)< \infty$ and $G(j, v) < G(j-1, v)$}{
		$\mathcal{X} \gets \mathcal{X}\cup\{j\}$\; 
		$v \gets v -  \Delta_j(v)$\;
	}
}
\Return{$\mathcal{X}$}
\end{algorithm}

\begin{theorem}[Validity of Algorithm \ref{ellisDP3}]
Algorithm \ref{ellisDP3} produces a $(1 - \varepsilon)$-optimal application portfolio for Ellis's problem.% in $O(D m + m \log m)$ time and $O(D m)$ space, where $D$ is the product of the denominators of the $f_j$-values.
\end{theorem}

\begin{proof}
%Let $\mathcal{W}$ denote the output of Algorithm \ref{ellisDP3} and $\mathcal{X}$ the true optimum. In the main loop, each time the target valuation $v$ is updated using
Because $\Delta_j(v)$ is rounded down, if $j \in \mathcal{W}[j, v]$, then the true value of $(1 - f_j) v\bigl(\mathcal{W}[j-1, v- \Delta_j(v)]\bigr) + f_j t_j$ may exceed the fixed-point value $v$ of $\mathcal{W}[j, v]$, but not by more than $10^{-P}$. This error accumulates with each school added to $\mathcal{W}$, but the number of additions is at most $m$. Therefore, where $v^*(\mathcal{W})$ denotes the fixed-point valuation of $\mathcal{W}$ as recorded in the algorithm, 
\begin{equation}
v(\mathcal{W}) - v^*(\mathcal{W}) \leq m 10^{-P} 
\end{equation}
We can define $v^*(\mathcal{X})$ analogously as the fixed-point valuation of $\mathcal{X}$ when its elements are added in index order and its value is updated and rounded down at each addition in accordance with \eqref{solvemeforvwjvminusj}. For the same reason as above, 
$v(\mathcal{X}) - v^*(\mathcal{X}) \leq m 10^{-P}$.

Finally, by the trivial assumption that all $g_j \leq H$, we know $v(\mathcal{X}) \geq v(\{m\}) = f_m t_m$. From this we obtain
\begin{equation}
\begin{split}
v(\mathcal{W}) &\geq v^*(\mathcal{W}) \geq v^*(\mathcal{X})
\geq v(\mathcal{X}) - m 10^{-P} \\
&\geq \left(1 - \frac{m 10^{-P}}{f_m t_m}\right) v(\mathcal{X})
\geq \left(1 - \varepsilon\right) v(\mathcal{X})
\end{split}
\end{equation}
which completes the proof. 
\end{proof}

\begin{theorem}[Computational complexity of Algorithm \ref{ellisDP3}]
Algorithm \ref{ellisDP3} uses $O(m /\varepsilon + m \log m)$ time and $O(m/\varepsilon)$ space, where $D$ is the product of the denominators of the $f_j$-values.
\end{theorem}

% To make this fully polynomial, need to get rid of the f_m t_m business ...
\begin{proof}
In the worst case, the number of indices at which $G(j, v)$ is evaluated is $O(|\mathcal{V}| m)$. Since
\begin{equation}
|\mathcal{V}| = t_m 10^{P} = t_m10^ { \bigl\lceil\log_{10}\left(m / \varepsilon f_m t_m\right)\bigr\rceil}
%\leq {\text{const.}}/{\varepsilon}
\end{equation}
is $O(1/ \varepsilon)$, adding the $O(m \log m)$-time required to sort $t$ yields the result. By recording the values of $G(j, v)$ in a dictionary as they are computed, we prevent redundant recursive calls at a cost of $O(|\mathcal{V}| m) = O(m / \varepsilon)$ space.
\end{proof}

>>>>

\usepackage{hyperref}
\hyperbaseurl{}
\urlstyle{same}
\usepackage[ruled,linesnumbered]{algorithm2e}
\newcommand{\lIfElse}[3]{\lIf{#1}{#2 \textbf{else}~#3}}

@@

An intuitive extension of the greedy algorithm for Alma's problem is to iteratively add to $\mathcal{X}$ the school $k$ for which $[ v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) ] / g_k$ is largest. However, this algorithm offers no guaranteed approximation ratio, as the following example shows.
\begin{example}
Let $t = (2, 2022)$, $f = (1, 1)$, $g = (1, 10000)$, and $H = 10000$. Then the greedy approximation algorithm produces a clearly inoptimal solution.
\end{example} 
% as the following example suggests ...The construction above shows that the objective function of Ellis's problem can approximate that of a knapsack problem with arbitrary precision, and this algorithm

\subsection{Pseudopolynomial-time dynamic program}
In this subsection, we assume, with minimal loss of generality, that $g_j \in \mathbb{N}$ for $j = 1\dots m$ and $H \in\mathbb{N}$, and provide an algorithmic solution to Ellis's problem that runs in $O(Hm + m\log m)$ time and $O(Hm)$ space. The algorithm resembles a familiar dynamic programming algorithm for the binary knapsack problem. Because we cannot assume that $H \leq m$ (as was the case in Alma's problem), this represents a pseudopolynomial-time solution (Dantzig 1957; Garey and Johnson 1979; \emph{Wikipedia}, s.v. ``Knapsack problem'').

For $j = 0 \dots m$ and $h = 0 \dots H$, let $\mathcal{X}[j, h]$ denote the optimal portfolio using only the schools $\{ 1, \dots, j\}$ and costing no more than $h$, and let $V[j,h] = v(\mathcal{X}[j, h])$.  It is clear that if $j=0$ or $h=0$, then $\mathcal{X}[j, h] = \O$ and $V[j, h] = 0$.  For convenience, we also define $V[j, h] = -\infty$ for all $h < 0$.

@@

\begin{proof}
Optimality follows from the foregoing discussion. Sorting $t$ is $O(m \log m)$.  The number of indices at which $V(j, h)$ is nontrivially defined is $O(Hm)$. To prevent redundant calls in the recursive function $V(j, h)$, its values must be stored in a dictionary as they are computed; this dictionary’s size is $O(Hm)$. 
\end{proof}

@@

\subsection{Fully polynomial-time approximation scheme}
As with the knapsack problem, Ellis's problem admits a complementary dynamic program that iterates on the value of the cheapest portfolio instead of on the cost of the most valuable portfolio. We will use this algorithm as the basis for a fully polynomial-time approximation scheme for Ellis's problem that uses $O(m^3 / \varepsilon)$ time and space. Here we assume, with minimal loss of generality, that each $t_j$ is integral.
%Now, we modify Algorithm \ref{ellisDP2} into a fully polynomial-time approximation scheme for Ellis's problem.

We will represent the approximate value of portfolios using a fixed-point decimal with a precision of $P$, where $P$ is the number of digits to retain after the decimal point. Let $r[x] = \lfloor 10^P x \rfloor 10^{-P}$ denote the value of $x$ rounded down to its nearest fixed-point representation. Since $\bar U = \sum_{j\in \mathcal{C}} f_j t_j$ is an upper bound on the value of any portfolio, the set of possible approximate portfolio valuations $\mathcal{V}$ is finite:
\begin{equation}
\mathcal{V} = \Bigl\{0, 1\times 10^{-P}, 2\times 10^{-P}, \dots, r\bigl[\bar U- 1\times 10^{-P}\bigr], r\bigl[\bar U\bigr], r\bigl[\bar U+ 1\times 10^{-P}\bigr]\Bigr\}
\end{equation}
Then $|\mathcal{V} | = \bar U \times 10^P + 2$.

For the remainder of this subsection, unless otherwise specified, the word \emph{value} refers to a portfolio’s value within the fixed-point framework, with the understanding that this is an approximation. We will account for the approximation error below when we prove the dynamic program’s validity.

For integers $0 \leq j \leq m$ and $v \in [-\infty, 0) \cup \mathcal{V}$, let $\mathcal{W}[j, v]$ denote the least expensive portfolio that uses only schools $\{ 1, \dots, j\}$ and has value at least $v$, if such a portfolio exists. Denote its value by $G[j, v] = r\bigl[v(\mathcal{W}[j, v])\bigr]$, where $G[j, v] = \infty$ if $\mathcal{W}[j, v]$ does not exist. It is clear that if $v \leq 0$, then $\mathcal{W}[j, v] = \O$ and $G[j, h] = 0$, and that if $j = 0$ and $v > 0$, then $G[j, h] = \infty$.  For the remaining indices (where $j, v > 0$), we claim that
\begin{align} \label{recursionrelationforcostmindp}
G[j, v] &=
\begin{cases}
\infty, \quad & t_j < v \\
\min\bigl\{G[j-1, v], g_j + G[j-1, v - \Delta_j(v)] \bigr\}, \quad & t_j \geq v 
%\begin{cases}
%\min\bigl\{G[j-1, v], g_j + G[j-1, v - \Delta] \bigr\}, \quad &f_j < 1 \\
%\min\bigl\{G[j-1, v], g_j \bigr\}, \quad &f_j = 1 \text{ and } f_j t_j \geq v\\
%G[j-1, v], \quad &f_j = 1 \text{ and } f_j t_j < v
\end{cases}\\
\text{where}\qquad
\Delta_j (v) &= 
\begin{cases}
r\left[\frac{f_j}{1 - f_j} (t_j - v)\right], \quad & f_j < 1\\
\infty, &f_j = 1
\end{cases} \label{deltajvdef}
\end{align}
In the $t_j < v$ case, any feasible portfolio must be composed of schools with utility less than $v$, and therefore its valuation can not equal $v$, meaning that $\mathcal{W}[j, v]$ is undefined. In the $t_j \geq v$ case, the first argument to $\min\{\}$ says simply that omitting $j$ and choosing $\mathcal{W}[j-1, v]$ is a permissible choice for $\mathcal{W}[j, v]$. If, on the other hand, $j \in \mathcal{W}[j, v]$, then
\begin{equation} \label{solvemeforvwjvminusj}
v(\mathcal{W}[j, v]) = (1 - f_j )v(\mathcal{W}[j, v]\setminus \{j\}) + f_j t_j\end{equation}
Therefore, the subportfolio $\mathcal{W}[j, v]\setminus \{j\}$ must have a value of at least $v - \Delta$, where $\Delta$ satisfies $v = (1 - f_j )(v - \Delta) + f_j t_j $. When $f_j < 1$, the solution to this equation is $ \Delta = \frac{f_j}{1 - f_j} (t_j - v)$. By rounding this value down, we ensure that the true valuation of $\mathcal{W}[j, v]$ is \emph{at least} $v - \Delta$.

@@

Once $G[j, v]$ has been calculated at each index, the associated portfolio can be found by applying the observation that $\mathcal{W}[j, v]$ contains $j$ if and only if $G[j, v] < G[j-1, v]$. Then an approximate solution to Ellis's problem is obtained by computing the optimal objective value $\max\{ w: G[m, w] \leq H\}$ and corresponding portfolio.

\begin{algorithm}[H] 
%\DontPrintSemicolon
\caption{Fully polynomial-time approximation scheme for Ellis's problem.} \label{ellisDP3}
\KwData{Utility values $t \in \mathbb{N}^m$, admissions probabilities $f \in (0, 1]^m$, application costs $g \in (0, \infty)^m$, budget $H \in (0, \infty)^m$, tolerance $\varepsilon \in (0, 1)$.}
Index schools in ascending order by $t$\;
Set precision $P \gets \bigl\lceil\log_{10}\left(m^2 / \varepsilon \bar U\right)\bigr\rceil$\;
\SetKwProg{Fn}{function}{ do}{end}
\Fn{$G(j, v)$}{
	\lIf{$v \leq 0$}{\Return{$0$}}
	\lElseIf{$j=0$ or $t_j < v$}{\Return{$\infty$}}
	\lElse {\Return{$\min\bigl\{ G(j-1, v), g_j + G\bigl(j-1, v -  \Delta_j(v)\bigr) \bigr\}$}}
}
$v\gets  \max\{ w: G(m, w) \leq H\}$\; \label{vrecordedhere}
$\mathcal{X} \gets \O$\;
\For{$j = m, m-1, \dots, 1$}{
	\If{$G(j, v)< \infty$ and $G(j, v) < G(j-1, v)$}{
		$\mathcal{X} \gets \mathcal{X}\cup\{j\}$\; 
		$v \gets v -  \Delta_j(v)$\;
	}
}
\Return{$\mathcal{X}$}
\end{algorithm}

\begin{theorem}[Validity of Algorithm \ref{ellisDP3}]
Algorithm \ref{ellisDP3} produces a $(1 - \varepsilon)$-optimal application portfolio for Ellis's problem. It uses $O(m^3 /\varepsilon)$ time and $O(m^3/\varepsilon)$ space.
% in $O(D m + m \log m)$ time and $O(D m)$ space, where $D$ is the product of the denominators of the $f_j$-values.
\end{theorem}

\begin{proof}
(Optimality.) Let $\mathcal{W}$ denote the output of Algorithm \ref{ellisDP3} and $\mathcal{X}$ the true optimum. We know that $v(\mathcal{X}) \leq \bar U$, and because each singleton portfolio is feasible, $\mathcal{X}$ must be more valuable than the average singleton portfolio; that is, $v(\mathcal{X}) \geq \bar U / m$.

% In the main loop, each time the target valuation $v$ is updated using
Because $\Delta_j(v)$ is rounded down in the recursion relation defined by \eqref{recursionrelationforcostmindp} and \eqref{deltajvdef}, if $j \in \mathcal{W}[j, v]$, then the true value of $(1 - f_j) v\bigl(\mathcal{W}[j-1, v- \Delta_j(v)]\bigr) + f_j t_j$ may exceed the fixed-point value $v$ of $\mathcal{W}[j, v]$, but not by more than $10^{-P}$. This error accumulates with each school added to $\mathcal{W}$, but the number of additions is at most $m$. Therefore, where $v^*(\mathcal{W})$ denotes the fixed-point valuation of $\mathcal{W}$ recorded in line \ref{vrecordedhere} of the algorithm, 
$v(\mathcal{W}) - v^*(\mathcal{W}) \leq m 10^{-P}$.

We can define $v^*(\mathcal{X})$ analogously as the fixed-point valuation of $\mathcal{X}$ when its elements are added in index order and its value is updated and rounded down at each addition in accordance with \eqref{solvemeforvwjvminusj}. By the same logic, 
$v(\mathcal{X}) - v^*(\mathcal{X}) \leq m 10^{-P}$. The optimality of $\mathcal{W}$ in the fixed-point environment implies that $v^*(\mathcal{W}) \geq v^*(\mathcal{X})$.

Applying these observations, we have
%the fact that $\bar U / m \leq v(\mathcal{X} \leq \bar U$, we have
\begin{equation}
\begin{split}
v(\mathcal{W}) &\geq v^*(\mathcal{W}) \geq v^*(\mathcal{X})
\geq v(\mathcal{X}) - m 10^{-P}
%\\&
\geq \left(1 - \frac{m^2 10^{-P}}{\bar U}\right) v(\mathcal{X})
\geq \left(1 - \varepsilon\right) v(\mathcal{X})
\end{split}
\end{equation}
which establishes the approximation bound.

(Computational resources.) In the worst case, the number of indices at which $G(j, v)$ is evaluated is $O(|\mathcal{V}| m)$. Since
\begin{equation}
|\mathcal{V}| = \bar U \times 10^{P} + 2 = \bar U \times 10^ { \bigl\lceil\log_{10}\left(m ^2/ \varepsilon \bar U\right)\bigr\rceil} + 2
\leq\frac{m^2}{\varepsilon} \times \text{const.}
\end{equation}
is $O(m^2/ \varepsilon)$, the time complexity is as promised. To prevent redundant recursive calls to $G(j, v)$, we need to record its values in a dictionary as they are computed; the space required by the dictionary is $O(|\mathcal{V}| m) = O(m^3 / \varepsilon)$.
\end{proof}
